Ecological validity of detecting data fabrication in experimental studies.

### 2016-05-24 submission/manuscript.Rmd
Small update analysis script

---
title: "Ecological validity of detecting data fabrication in experimental studies."
author: "Chris HJ Hartgerink"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: pdf_document
csl: ../bibliography/apa.csl
bibliography: ../bibliography/library.bib
---
<!---

@@

### Results.
```{r prep data study 1, echo = FALSE}
options(digits = 20)
# Compute the summary statistics for Many Labs
# source('../functions/compute_summary_anch_ml.R')
source('functions/compute_summary_anch_ml.R')
# Process the collected, fabricated data
# source('../functions/process_qualtrics_anch_01.R')
source('functions/process_qualtrics_anch_01.R')

# Read the data
# ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
# qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml$stat_know <- NA
ml$spss <- NA
ml$rcran <- NA
ml$stata <- NA
ml$sas <- NA
ml$matlab <- NA
ml$python <- NA
ml$other <- NA
ml$nopro <- NA
ml$noanch <- NA
ml$rng <- NA
ml$full <- NA
ml$tries <- NA
ml$descr <- NA
ml$bonus <- NA
ml$type <- 'ml'
qualtrics$type <- 'qualtrics'

@@

```{r compile results for detecting data fabrication, echo = FALSE}
dat_summary_file <- 'data/study1_res.csv'

# conduct the analyses iteratively
for (pp in unique(dat$referrer))
{
  # Loop through each study to compute the ANOVA results
  for (j in 1:4)
  {
    indexor <- dat$referrer == pp & dat$study == j

@@

  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
  # Add the sigma sd observed per study (NOT PREREGISTERED)
  # Nog wijzigen adhv mva opmerkingen
  obs_sigma_sd_study1 <- sd(tilde_s2_1)
  obs_sigma_sd_study2 <- sd(tilde_s2_2)
  obs_sigma_sd_study3 <- sd(tilde_s2_3)
  obs_sigma_sd_study4 <- sd(tilde_s2_4)

  iter <- 100000
  s2 <- dat$anch_sd[dat$referrer == pp]^2
  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
  sim_sigma <- NULL

@@

```

library(ROCR)
data(ROCR.simple)
pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
perf <- performance(pred,"tpr","fpr")
plot(perf)

# Study 2

>>>>

---
title: "Ecological validity of detecting data fabrication in experimental studies."
author: "Chris HJ Hartgerink"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: pdf_document
csl: ../bibliography/apa.csl
bibliography: ../bibliography/library.bib
---

```{r prepwork, echo = FALSE}
if(!require(pROC)){install.packages('pROC')}
library(pROC)
if(!require(foreign)){install.packages('foreign')}
library(foreign)

# Compute the summary statistics for Many Labs
source('../functions/compute_summary_anch_ml.R')
# source('functions/compute_summary_anch_ml.R')
# Process the collected, fabricated data
source('../functions/process_qualtrics_anch_01.R')
# source('functions/process_qualtrics_anch_01.R')

# Read the data
ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
# ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
# qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)

dat_summary_file <- '../data/study1_res.csv'
```

@@

### Results.
```{r prep data study 1, echo = FALSE}
options(digits = 20)
ml$stat_know <- NA
ml$spss <- NA
ml$rcran <- NA
ml$stata <- NA
ml$sas <- NA
ml$matlab <- NA
ml$python <- NA
ml$other <- NA
ml$nopro <- NA
ml$noanch <- NA
ml$rng <- NA
ml$full <- NA
ml$tries <- NA
ml$descr <- NA
ml$bonus <- NA
ml$type <- 'ml'
qualtrics$type <- 'qualtrics'

@@

```{r compile results for detecting data fabrication, echo = FALSE}
# conduct the analyses iteratively
for (pp in unique(dat$referrer))
{
  # Loop through each study to compute the ANOVA results
  for (j in 1:4)
  {
    indexor <- dat$referrer == pp & dat$study == j

@@

  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))

  obs_sigma_sd_study1 <- sd(tilde_s2_1)
  obs_sigma_sd_study2 <- sd(tilde_s2_2)
  obs_sigma_sd_study3 <- sd(tilde_s2_3)
  obs_sigma_sd_study4 <- sd(tilde_s2_4)

  iter <- 10
  s2 <- dat$anch_sd[dat$referrer == pp]^2
  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
  sim_sigma <- NULL

@@

dat_summary <- read.csv(dat_summary_file)

tp <- NULL
fp <- NULL
fn <- NULL
tn <- NULL

i <- 1

for (threshold in seq(0, .1, .01))
{
  tp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
  fp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'ml', na.rm = TRUE)
  fn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
  tn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'ml', na.rm = TRUE)

  i <- i + 1
}

fpr <- fp / (fp + tn)
tpr <- tp / (tp + fp)
fnr <- fn / (fn + tp)
tnr <- tn / (tn + fn)
```

library(ROCR)
data(ROCR.simple)
pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
perf <- performance(pred,"tpr","fpr")
plot(perf)
--->
# Study 2
